Strong lensing selection effects

### 2022-08-23 paper/seleff.tex
fixed typo
added acknowledgements

In this section we study how the probability of a strong lensing event varies as a function of lens and source properties.
In order to do so, it is useful to introduce the concept of strong lensing cross-section.
Given a foreground galaxy with parameters $\psilens$, a background source with parameters $\psisource$, and a criterion $S$ to define a strong lensing event, the strong lensing cross-section is defined as \citep{Son22}:
\begin{equation}\label{eq:crosssect}
\crosssect = \int_{\mathbb{R}^2} d\boldsymbol\beta \pdet(\psilens,\psisourcenobeta,\boldsymbol\beta|S),
\end{equation}
where $\boldsymbol\beta$ is the position of the background source, $\psisourcenobeta$ is the ensemble of source parameter except for the position, and the integral is carried out over the whole sky.
The definition above is valid for both a point source and an extended source: although there is no unique way of defining the position of an extended source, the integral over the sky ensures that the result is independent of how the source position is defined.
In the limit of low density of background sources, which is satisfied in all practical cases, the probability of a lensing event is proportional to $\crosssect$.
The lensing cross-section defined via \Eref{eq:crosssect} depends solely on the lens detection probability $\pdet$ and does not take into account whether the lens can be correctly classified by a lens finder.
This separate selection step is captured by the term $\pfind$ in \Eref{eq:two}.
In this section we consider solely on the detectability of a lens, and therefore focus only on $\crosssect$. In \Sref{sect:lenspop}, when considering specific lens survey simulations, we introduce $\pfind$.

@@

%\begin{acknowledgements}

%\end{acknowledgements}

>>>>

In this section we study how the probability of a strong lensing event varies as a function of lens and source properties.
In order to do so, it is useful to introduce the concept of strong lensing cross-section.
Given a foreground galaxy with parameters $\psilens$, a background source with parameters $\psisource$, and a criterion $S$ to define a strong lensing event, the strong lensing cross-section is defined as \citep{Son22}:
\begin{equation}\label{eq:crosssect}
\crosssect = \int_{\mathbb{R}^2} d\boldsymbol\beta \pdet(\psilens,\psisourcenobeta,\boldsymbol\beta|S),
\end{equation}
where $\boldsymbol\beta$ is the position of the background source, $\psisourcenobeta$ is the ensemble of source parameter except for the position, and the integral is carried out over the whole sky.
The definition above is valid for both a point source and an extended source: although there is no unique way of defining the position of an extended source, the integral over the sky ensures that the result is independent of how the source position is defined.
In the limit of low density of background sources, which is satisfied in all practical cases, the probability of a lensing event is proportional to $\crosssect$.
The lensing cross-section defined via \Eref{eq:crosssect} depends solely on the lens detection probability $\pdet$ and does not take into account whether the lens can be correctly classified by a lens finder.
This separate selection step is captured by the term $\pfind$ in \Eref{eq:two}.
In this section we consider exclusively the detectability of a lens, and therefore focus only on $\crosssect$. In \Sref{sect:lenspop}, when considering specific lens survey simulations, we introduce $\pfind$.

@@

\begin{acknowledgements}

The collaboration leading to this work was initiated at the 2022 Lorentz Center workshop “Bridging gaps between dynamical probes of galaxies”.

\end{acknowledgements}
